### 2013-04-01 doc/final_report/evaluation.tex
Finished evaluation

>>>>

\section{ Summary }

This chapter has discussed the achievements arising from the Partridge project:
the design and implementation of the paper preprocessor and the integrated
Artificial Intelligence; lessons learnt from developing Partridge's HTML5
interface and considerations needed to help users to understand complicated
applications; professional and personal development through my relationship
with my supervisors. Wider impacts of Partridge include a growing number of
users and interest from one of the larger research journals that Partridge
indexes.

Some of the limitations of Partridge are discussed above. These include the
additional paper classifiers which were omitted due to time constraints,
underlying problems with SAPIENTA and scalability in general. Future
development will deal with the issue of adding a recommendation engine to the
system and how this could be implemented.

Moreover, the possibility of further research into the relationship between
CoreSC and paper type is explored and I am hoping that my submission to the BCS
AI conference inspires others to carry out research in this area.

I have thoroughly enjoyed working on Partridge and feel that this project has
developed my ability to apply machine learning algorithms to practical
applications and my professional praxis. I hope to continue to develop
Partridge into a useful and widely used research tool and am also
greatly looking forward to submitting my paper to the BCS AI Conference and
continuing my professional collaboration with Dr Clare and Dr Liakata.
